Wrap Around

### 2024-04-01 scripts/00.1_wrapAround.qmd
added vertices to deal with the no-edges problem

  # make graph from sri
  message("making graph")
  g_fl <- makeGraph(mode = "sri", data = fl, weighted = T)
  g_fe <- makeGraph(mode = "sri", data = fe, weighted = T)
  g_ro <- makeGraph(mode = "sri", data = ro, weighted = T)

>>>>

  # make graph from sri
  message("making graph")
  verts <- unique(rotated$Nili_id)
  g_fl <- makeGraph(mode = "sri", data = fl, weighted = T, vertices = verts)
  g_fe <- makeGraph(mode = "sri", data = fe, weighted = T, vertices = verts)
  g_ro <- makeGraph(mode = "sri", data = ro, weighted = T, vertices = verts)
